---
title: "Harvard Student Emoji Usage"
author: "Linda Qin"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(magrittr)
library(DataCombine)
library(tidyverse)

emoticons <- read.csv("emoji_decoder.csv", header = T)
```

```{r Data, echo=FALSE}

emoji_data <- read_csv("./raw-data/emoji-responses.csv", 
                       col_types = cols(
                          Timestamp = col_character(),
                          `Please confirm that you are filling out this form on an iPhone before moving on with this study.` = col_character(),
                          `Graduation Year` = col_double(),
                          Gender = col_character(),
                          `What house do you live in?` = col_character(),
                          `What best describes your ethnicity?` = col_character(),
                          `Where is your hometown / current residence area outside of Harvard located?` = col_character(),
                          `(Intended) Concentration(s)` = col_character(),
                          `Secondary (if applicable)` = col_character(),
                          `Email Address` = col_character()
                       ))

emoji_data_count <- nrow(emoji_data)

# Renaming Columns

emoji_data %<>% 
  rename(time = "Timestamp",
         confirm = "Please confirm that you are filling out this form on an iPhone before moving on with this study.",
         emojis = "Type, in order, the first two columns from your 'frequently used' emoji section.",
         year = "Graduation Year",
         gender = "Gender",
         house = "What house do you live in?",
         ethnicity = "What best describes your ethnicity?",
         state = "Where is your hometown / current residence area outside of Harvard located?",
         concentration = "(Intended) Concentration(s)",
         secondary = "Secondary (if applicable)",
         email = "Email Address")

```


## About This Project

### The World of Emojis

Emojis have changed the way people communicate digitally in the 21st century, so much so that, in 2015, Oxford Dictionary's Word of the Year was not even a word, but an emoji ( `r emo::ji("face with tears of joy")`). Currently, there are 3,178 emojis in the Unicode Standard, with 117 new emojis slated to enter in 2020. With such a large number of possibilities, how do people choose which emojis to use when expressing their feelings? What is the difference between `r emo::ji("grin")`and `r emo::ji("beaming face with smiling eyes")`, and how is meaning ascribed to `r emo::ji("slightly smiling face")` vs `r emo::ji("upside_down_face")`? 

While this study will not be able to answer all these questions fully, I aim to conduct an in-depth exploration of the connection between different internal and external traits of people and their emoji preferences and tendencies, specifically amongst the Harvard population.

This project was inspired by a [Tableau visualization](https://public.tableau.com/views/TheEmojiofSpotifyArtists/DescribeArtists?:embed=y&:display_count=y&:origin=viz_share_link) created by Spotify that analyzed public user-generated playlists for the most distinctive emoji use by artist.

### Data Collection

Emoji preference data was collected through a short, 1-minute survey, [linked here](https://forms.gle/RkFXovkt3fNKgfga8). The breakdown of the survey is as follows:
- Confirmation that the user is responding on an iPhone
- A single-line input asking for the user’s first two columns of their frequently-used emoji section (in order)
- Demographic information, such as year, gender, ethnicity and concentration

Responses to the survey were collected from the Harvard undergraduate community through various social circles, commons classes such as Gov1005, and house email lists. Currently, `r emoji_data_count` individuals have responded, with the goal of reaching at least 100 by the end of the survey period.

<b>Update:</b> So far, I have updated the data with the newest entries. Due to thesis work, I have not been able to analyze the data outside of ongoing data collection.

#### Noise in Data

A difficulty in collecting emoji preferences is the question of how to measure this in an objective way. I decided to limit participants to iPhone users because Apple has a standard formula of calculating its ‘frequently used emojis’ section. This provides a more quantitative method of understanding emoji use, rather than asking for the respondents’ own perception of their use. As Apple’s ‘frequently used emojis’ section is actually a mix of both frequently and recently used emojis, the responses were limited to the first two columns of the section (as Apple has indicated this as the ordering of emoji frequency). However, there is still the possibility of noise in this data from the (seeping in) of recently used emojis, such as a respondent who had Ice + Land in her response due to her recent messages about a spring break trip to Iceland. 

Furthermore, due to the limited reach of the author, the sample of students is not representative of the general Harvard community – there are demographics skews, as well as the existence of a selection bias from limiting responses to iPhone owners. However, this study is meant to highlight interesting and unexpected correlations in emoji use, rather than explain causal behaviors; please take all of this with a grain of salt.

### About Linda Qin

Linda is a senior in Winthrop House studying Computer Science & Mind, Brain and Behavior, with a secondary in Economics. Her favorite emoji is `r emo::ji("new moon face")`, and the rest of her bio can be summed up very nicely by her most frequently used emojis: `r emo::ji("smiling face with smiling eyes")` `r emo::ji("pleading_face")` `r emo::ji("eyes")` `r emo::ji("woman gesturing OK")` `r emo::ji("loudly crying face")` `r emo::ji("sneezing face")` `r emo::ji("smiling_face_with_3_hearts")` `r emo::ji("grinning face with sweat")` `r emo::ji("peace")` `r emo::ji("heavy_heart_exclamation")`.

```{r}
emoji_data
```

```{r Add Space Between Each Character}
emoji_data$emojis <- sub("\\s+$", "", gsub('(.{1})', '\\1 ', emoji_data$emojis))
```

```{r Remove Double Spaces}

# Turn to normal data frame to work with

emoji_data <- as.data.frame(emoji_data)

emoji_data$emojis <- gsub("  ", "", emoji_data$emojis)

```

```{r}
emoji_data
```


```{r Separate into Different Columns}
 
emoji_data %<>%
  separate(emojis, 
           c("e1", "e2", "e3", "e4", "e5", "e6", "e7", "e8", "e9", "e10", "other"), 
           sep = c(1,2,3,4,5,6,7,8,9,10), 
           remove = FALSE)

```

```{r}
rankings <- emoji_data %>%
  group_by(e1) %>%
  count(e1) %>%
  arrange(desc(n))
```

```{r}
rankings
```


```{r New Replace}
emojireplace <- FindReplace(data = emoji_data, Var = "emojis", 
                            replaceData = emoticons,
                            from = "modified_r", to = "tag", 
                            exact = FALSE)
```

```{r Failed Conversion}

emoji_data$emojis <- iconv(emoji_data$emojis, from = "latin1", to = "ascii", sub = "byte")

```

```{r Failed Replacements to Match}

# change U+1F469 U+200D U+1F467 to \U1F469\U200D\U1F467

emoticons$Codepoint <- gsub("\\+", "000", emoticons$Codepoint)

# tried to add a space with a backslash but can't get it to work

# test <- gsub("\U", " ", "\U0001f440\U0001f646", fixed = TRUE)
  

```

```{r Failed Remove Spaces Dictionary}
emoticons$tag %<>%
  str_replace_all(" ", "")
```

```{r Failed Add Space}

emoticons$tag <- lapply(emoticons$tag, function(x) paste0(x, " "))

```

```{r Failed Replace Old System with New}
emojireplace <- FindReplace(data = emoji_data, Var = "emojis", 
                            replaceData = emoticons,
                            from = "ftu8", to = "utf8", 
                            exact = FALSE)
```

```{r Failed Replace with Tag}
emojireplace <- FindReplace(data = emoji_data, Var = "emojis", 
                            replaceData = emoticons,
                            from = "utf8", to = "tag", 
                            exact = FALSE)

```
